# Various Functions

## Unlist Unname

```{r Unlist Unname}
uln <- function(string){
  return(unname(unlist(string)))
}
```

## Unique Unlist Unname

```{r Unlist Unname}
uuln <- function(string){
  return(unique(unname(unlist(string))))
}
```

## Taxa ASV Level

```{r Taxa ASV Level}
if.asv <- function(taxa.level){
  if(taxa.level=="ASV"){
    asv <- TRUE
    taxa.level <- "Species"
  }else{
    asv <- FALSE
  }
  return(c(taxa.level, asv))
}
```

## Add Families to Phyloseq

```{r}
add.families.phyloseq <- function(phyloseq){
  sample.table <- sample.to.data.frame(phyloseq)
  sample.table[, "family"] <- as.numeric(gsub('[a-z]*', "", gsub('[A-Z]*', "", sapply(row.names(sample.table), function(x) strsplit(x, "_")[[1]][1]))))
  sample_data(phyloseq) <- sample.table
  return(phyloseq)
}
```

## Add Families to Phyloseq

```{r}
add.families.dataframe <- function(dataframe){
  dataframe[, "family"] <- as.numeric(gsub('[a-z]*', "", gsub('[A-Z]*', "", sapply(row.names(dataframe), function(x) strsplit(x, "_")[[1]][1]))))
  return(dataframe)
}
```

## Identify Families

```{r Identify Families}
identify.families <- function(object){
  if(class(object)=="phyloseq"){
    return(as.character(sort(as.numeric(as.character(unique(unlist(as.data.frame(sample_data(object))[, "family"])))))))
  }else if(class(object)=="data.frame"){
    return(as.character(sort(as.numeric(as.character(unique(unlist(object[, "family"])))))))
  }
}
```

## Identify Type

```{r}
identify.type <- function(phyloseq){
  return(uuln(sample_data(phyloseq)[, "type"]))
}
```

## Row name

```{r}
row.name <- function(object, cell, column=NA){
  if(class(object)=="phyloseq"){
    samdf <- data.frame(sample_data(object))
    if(is.na(column)){
      for(a in 1:ncol(samdf)){
        if(cell %in% samdf[, a]){
          row.name <- rownames(samdf)[c(which(samdf[, a]==c(cell)))]
        }
      }
    }else{
      row.name <- rownames(samdf)[c(which(samdf[, column]==c(cell)))]
    }
  }else if(class(object)=="data.frame"){
    if(is.na(column)){
      for(a in 1:ncol(object)){
        if(cell %in% object[, a]){
          row.name <- rownames(object)[c(which(object[, a]==c(cell)))]
        }
      }
    }else{
      row.name <- rownames(object)[c(which(object[, column]==c(cell)))]
    }
  }
  return(row.name)
}
```

## Do Adonis

```{r}
doadonis<- function(phyloseq, distance=distance, factor) {
        bdist <- phyloseq::distance(phyloseq, distance)
        col <- as(sample_data(phyloseq), "data.frame")[, factor]
        # Adonis test
        adonis.bdist <- vegan::adonis(unname(bdist) ~ col)
        p <- signif(as.data.frame(adonis.bdist[1])$aov.tab.Pr..F.[1], digits=2)
        r2 <- signif(as.data.frame(adonis.bdist[1])$aov.tab.R2[1], digits=2)
        
              cat("\n      ", paste("p=", p))
        res <- c(p, r2)
        return(res)
      }
```

## Subset Object *************

```{r Subset Object}
subset.object <- function(object, pheno, col.name=NULL, remove=FALSE){
        # cat("\n  ", paste("Subset sample data by", pheno))
  if(class(object)=="phyloseq"){
      if(length(pheno)==1){
      samdf <- data.frame(sample_data(object))
      if(is.null(col.name)){
        if(remove==FALSE){
          for(a in 1:ncol(samdf)){
            if(pheno %in% samdf[, a]){
              sample_data(object) <- sample_data(object)[c(which(sample_data(object)[, a]==c(pheno))), ]
            }
          }
        }else if(remove==TRUE){
          for(a in 1:ncol(samdf)){
            if(pheno %in% samdf[, a]){
              sample_data(object) <- sample_data(object)[c(which(sample_data(object)[, a]!=c(pheno))), ]
            }
          }
        }
      }else{
        if(remove==FALSE){
          sample_data(object) <- sample_data(object)[c(which(sample_data(object)[, col.name]==c(pheno))), ]
        }else if(remove==TRUE){
          sample_data(object) <- sample_data(object)[c(which(sample_data(object)[, col.name]!=c(pheno))), ]
        }
      }
      if(length(which(taxa_sums(object)!=0))!=0){
        object <- prune_taxa(taxa_sums(object)!=0, object)
      }
    }else{
      phyloseq.list <- list()
      object.sub <- object
      for(a in 1:length(pheno)){
        samdf <- data.frame(sample_data(object))
        if(is.null(col.name)){
          if(remove==FALSE){
            object.sub <- object
            for(b in 1:ncol(samdf)){
              if(pheno[a] %in% samdf[, b]){
                sample_data(object.sub) <- sample_data(object)[c(which(sample_data(object)[, b]==c(pheno[a]))), ]
              }
            }
          }else if(remove==TRUE){
            for(a in 1:ncol(samdf)){
              if(pheno[a] %in% samdf[, b]){
                sample_data(object.sub) <- sample_data(object)[c(which(sample_data(object)[, b]!=c(pheno[a]))), ]
              }
            }
          }
        }else{
          if(remove==FALSE){
            if(pheno[a] %in% samdf[, col.name]){
              if(exists("check.for.exist")==FALSE){
                check.for.exist <- a
              }
              object.sub <- object
              sample_data(object.sub) <- sample_data(object)[c(which(sample_data(object)[, col.name]==c(pheno[a]))), ]
            }
          }else if(remove==TRUE){
            sample_data(object.sub) <- sample_data(object)[c(which(sample_data(object)[, col.name]!=c(pheno[a]))), ]
          }
        }
        if(remove==FALSE){
          if(length(which(taxa_sums(object.sub)!=0))!=0){
            phyloseq.list[[a]] <- prune_taxa(taxa_sums(object.sub)!=0, object.sub)
          }else{
            phyloseq.list[[a]] <- object.sub
          }
          if(exists("check.for.exist")==TRUE){
              if(a!=check.for.exist){
              phyloseq.list[[check.for.exist]] <- merge_phyloseq(phyloseq.list[[check.for.exist]], phyloseq.list[[a]])
            }
          }
        }
      }
      if(remove==FALSE){
        if(exists("check.for.exist")==TRUE){
          object <- phyloseq.list[[check.for.exist]]
          if(length(which(taxa_sums(object)!=0))!=0){
            object <- prune_taxa(taxa_sums(object)!=0, object)
          }
        }
      }else if(remove==TRUE){
        object <- object.sub
        if(length(which(taxa_sums(object)!=0))!=0){
          object <- prune_taxa(taxa_sums(object)!=0, object)
        }
      }
    }
  }else if(class(object)=="data.frame"){
    object.og <- object
    if(is.null(col.name)){
      if(remove==FALSE){
        if(length(pheno)>1){
          for(a in 1:length(pheno)){
            for(b in 1:ncol(object)){
              if(pheno %in% object[, b]){
                merge.object <- object.og[c(which(object.og[, b]==c(pheno[a]))), ]
              }
            }
            if(a==1){
              object <- merge.object
            }else{
              object <- rbind(object, merge.object)
            }
          }
        }else{
          for(a in 1:ncol(object)){
            if(pheno %in% object[, a]){
              object <- object[c(which(object[, a]==c(pheno))), ]
            }
          }
        }
      }else if(remove==TRUE){
        for(a in 1:ncol(object)){
          if(pheno %in% object[, a]){
            object <- object[c(which(object[, a]!=c(pheno))), ]
          }
        }
      }
    }else{
      if(remove==FALSE){
        if(length(pheno)>1){
          for(a in 1:length(pheno)){
            merge.object <- object.og[c(which(object.og[, col.name]==c(pheno[a]))), ]
            if(a==1){
              object <- merge.object
            }else{
              object <- rbind(object, merge.object)
            }
          }
        }else{
          object <- object[c(which(object[, col.name]==c(pheno))), ]
        }
      }else if(remove==TRUE){
        if(length(pheno)>1){
          for(a in 1:length(pheno)){
            object <- object[c(which(object[, col.name]!=c(pheno[a]))), ]
          }
        }else{
          object <- object[c(which(object[, col.name]!=c(pheno))), ]
        }
      }
    }
  }
  
  return(object)
}
```

## Replace NAN

```{r Replace NAN}
replace.nan <- function(dataframe, value){
  dataframe[is.nan(dataframe)] <- value
  return(dataframe)
}
```

## Remove NAN

```{r}
remove.nan <- function(object, column=NA){
  if(class(object)=="data.frame"){
    if(!is.nan(column)){
      if(length(which(is.nan(object[, column])==FALSE))!=nrow(object)){
        object <- object[-c(which(is.nan(object[, column])==TRUE)), ]
      }
    }else{
      for(a in 1:length(ncol(object))){
          if(length(which(is.nan(object[, a])==FALSE))!=nrow(object)){
          object <- object[-c(which(is.nan(object[, a])==TRUE)), ]
        }
      }
    }
  }else if(class(object)=="list"){
    for(a in 1:length(list)){
      if(length(which(is.nan(object)==FALSE))!=length(object)){
        object <- object[-c(which(is.nan(object)==TRUE))]
      }
    }
  }
  return(object)
}
```

## Replace NA

```{r Replace NA}
replace.na <- function(dataframe, value){
  dataframe[is.na(dataframe)] <- value
  return(dataframe)
}
```

## Remove NA

```{r}
remove.na <- function(object, column=NA){
  if(class(object)=="data.frame"){
    if(!is.na(column)){
      if(length(which(is.na(object[, column])==FALSE))!=nrow(object)){
        object <- object[-c(which(is.na(object[, column])==TRUE)), ]
      }
    }else{
      for(a in 1:length(ncol(object))){
          if(length(which(is.na(object[, a])==FALSE))!=nrow(object)){
          object <- object[-c(which(is.na(object[, a])==TRUE)), ]
        }
      }
    }
  }else if(class(object)=="list" || class(object)=="character"){
    if(length(which(is.na(object)==FALSE))!=length(object)){
      object <- object[-c(which(is.na(object)==TRUE))]
    }
  }else if(class(object)=="phyloseq"){
    object.frame <- sample.to.data.frame(object)
    non.na <- row.names(object.frame[c(which(is.na(object.frame[, column])==FALSE)), ])
    object <- prune_samples(non.na, object)
  }
  return(object)
}
```


## Remove duplicated

```{r}
remove.duped <- function(list){
  return(list[-c(which(duplicated(list)))])
}
```


## Replace 0

```{r Replace 0}
replace.0 <- function(dataframe, value){
  dataframe[dataframe==0] <- value
  return(dataframe)
}
```

## Remove 0

```{r}
remove.0 <- function(data.frame, column){
  if(length(which(data.frame[, column]==0))!=nrow(data.frame)){
    data.frame <- data.frame[-c(which(data.frame[, column]==0)), ]
  }
  return(data.frame)
}
```

## Remove taxa under 

```{r}
remove.taxa.under <- function(phyloseq, value){
  phyloseq <- prune_taxa(taxa_sums(phyloseq)>value, phyloseq)
  return(phyloseq)
}
```


## Replace Specific

```{r Replace 0}
replace.specific <- function(list, value, replacement){
  list[list==value] <- replacement
  return(list)
}
```

## ASV to Taxa

```{r}
asv.to.taxa <- function(phyloseq, asv, taxa.level){
  if(length(asv)>1){
    taxa <- c()
    for(a in 1:length(asv)){
      taxa[a] <- uln(data.frame(tax_table(phyloseq))[which(rownames(data.frame(tax_table(phyloseq)))==asv[a]), taxa.level])
    }
  }else{
    taxa <- uln(data.frame(tax_table(phyloseq))[which(rownames(data.frame(tax_table(phyloseq)))==asv), taxa.level])
  }
  return(taxa)
}
```

## Taxa to ASV

```{r}
taxa.to.asv <- function(phyloseq, taxa, taxa.level){
  if(length(taxa)>1){
    asv <- c()
    for(a in 1:length(taxa)){
      asv[a] <- rownames(data.frame(tax_table(phyloseq)))[which(data.frame(tax_table(phyloseq))[, taxa.level]==taxa)]
    }
  }else{
    asv <- rownames(data.frame(tax_table(phyloseq)))[which(data.frame(tax_table(phyloseq))[, taxa.level]==taxa)]
  }
  return(asv)
}
```

## Count taxa

```{r}
count.taxa <- function(phyloseq){
  otu.frame <- otu.to.data.frame(phyloseq)
  count.frame <- data.frame(rowSums(otu.frame!=0))
  colnames(count.frame) <- "number of taxa"
  return(count.frame)
}
```


## Tax Table to Data Frame

```{r}
tax.to.data.frame <- function(phyloseq){
  return(data.frame(tax_table(phyloseq)))
}
```

## OTU Table to Data Frame

```{r}
otu.to.data.frame <- function(phyloseq){
  return(data.frame(otu_table(phyloseq)))
}
```

## Sample Data to Data Frame

```{r}
sample.to.data.frame <- function(phyloseq){
  return(data.frame(sample_data(phyloseq)))
}
```

## Combine Tax and OTU

```{r}
otu.tax <- function(phyloseq){
  tax.table <- tax.to.data.frame(phyloseq)
  otu.table <- otu.to.data.frame(phyloseq)
  combined.table <- merge(tax.table, t(otu.table), by="row.names")
  rownames(combined.table) <- combined.table[,"Row.names"]
  combined.table <- combined.table[,-c(1)]
  return(combined.table)
}
```

<!-- ## Combine Pheno and OTU -->

<!-- ```{r} -->
<!-- pheno.otu <- function(phyloseq){ -->
<!--   pheno.table <- sample.to.data.frame(phyloseq) -->
<!--   pheno.table[,"sample"] <- row.names(pheno.table) -->
<!--   otu.table <- otu.to.data.frame(phyloseq) -->
<!--   otu.table[,"samID"] <- rownames(otu.table) -->
<!--   combined.table <- merge(pheno.table, combined.table, by="samID") -->
<!--   colnames(combined.table)[1] <- "samples" -->
<!--   return(combined.table) -->
<!-- } -->
<!-- ``` -->


## Combine Pheno, Tax, and OTU

```{r}
pheno.otu.tax <- function(phyloseq){
  pheno.table <- sample.to.data.frame(phyloseq)
  pheno.table[,"sample"] <- row.names(pheno.table)
  # print(pheno.table)
  tax.table <- tax.to.data.frame(phyloseq)
  tax.table[,"asv"] <- rownames(tax.table)
  otu.table <- otu.to.data.frame(phyloseq)
  combined.table <- merge(tax.table, t(otu.table), by="row.names")
  rownames(combined.table) <- combined.table[,"Row.names"]
  combined.table <- combined.table[,-c(1)]
  combined.table <- as.data.frame(pivot_longer(combined.table, c(9:ncol(combined.table)), names_to="sample", values_to="value"))
  # row.names(combined.table) <- combined.table[,"sample"]
  # print(pheno.table)
  combined.table <- merge(pheno.table, combined.table, by="sample")
  colnames(combined.table)[1] <- "samples"
  return(combined.table)
}
```

## Merge multiple frames
```{r}
merge.multi.frames <- function(frame.list, by, all=FALSE){
  suppressWarnings(rm(merge.frame))
  for(a in 2:length(frame.list)){
    if(a==2){
      merge.frame <- merge(frame.list[[1]], frame.list[[a]], by=by, all=all)
    }else{
      merge.frame <- merge(merge.frame, frame.list[[a]], by=by, all=all)
    }
    if(length(by)==1){
      if(by=="row.names"){
        rownames(merge.frame) <- merge.frame[,c("Row.names")]
        merge.frame <- merge.frame[,-c(which.col.name(merge.frame, "Row.names"))]
      }
    }
  }
  return(merge.frame)
}
```


## Form reassignment 

```{r}
form.reassign <- function(data.frame){
  for(a in 1:nrow(data.frame)){
    if(data.frame[a, "form"]=="I"){
      data.frame[a, "form"] <- "Initial"
    }else if(data.frame[a, "form"]=="F1"||data.frame[a, "form"]=="F"){
      data.frame[a, "form"] <- "Follow up 1"
    }else if(data.frame[a, "form"]=="F2"){
      data.frame[a, "form"] <- "Follow up 2"
    }else if(data.frame[a, "form"]=="F3"){
      data.frame[a, "form"] <- "Follow up 3"
    }else if(data.frame[a, "form"]=="F4"){
      data.frame[a, "form"] <- "Follow up 4"
    }
  }
  return(data.frame)
}
```

## Sample type rename

```{r}
sample.type.rename <- function(phyloseq){
  for(a in 1:nrow(sample_data(phyloseq))){
    if(sample_data(phyloseq)[a, "type"]=="BNA"){
      sample_data(phyloseq)[a, "type"] <- "Infant nasal"
    }else if(sample_data(phyloseq)[a, "type"]=="BSA"){
      sample_data(phyloseq)[a, "type"] <- "Infant saliva"
    }else if(sample_data(phyloseq)[a, "type"]=="BST"){
      sample_data(phyloseq)[a, "type"] <- "Infant stool"
    }else if(sample_data(phyloseq)[a, "type"]=="MNA"){
      sample_data(phyloseq)[a, "type"] <- "Mother nasal"
    }else if(sample_data(phyloseq)[a, "type"]=="MSA"){
      sample_data(phyloseq)[a, "type"] <- "Mother saliva"
    }else if(sample_data(phyloseq)[a, "type"]=="MBM"){
      sample_data(phyloseq)[a, "type"] <- "Mother milk"
    }else if(sample_data(phyloseq)[a, "type"]=="MAS"){
      sample_data(phyloseq)[a, "type"] <- "Mother skin"
    }
  }
  return(phyloseq)
}
```

## Round to 5
```{r}
round.to.5 <- function(number){
  return((ceiling(number/5)*5))
}
```


# Sigfill
```{r}
sigfill <- function(values, sigfigs=2, as.p=FALSE){
  values <- uln(values)
  out <- c()
  if(!as.p){
    for(a in 1:length(values)){
      if(values[a]==1){
        out[a] <- paste0("1.", paste0(rep(0, sigfigs), collapse=""))
      }else if((values[a] < as.numeric(paste0("0.", paste0(rep(0, (sigfigs-1)), collapse=""), "1")))){
        out[a] <- paste0("<0.", paste0(rep(0, (sigfigs-1)), collapse=""), "1")
      }else{
        sig.dec <- (which(strsplit(as.character(values[a]), "")[[1]]==".")-1)+sigfigs
        out[a] <- formatC(round(values[a], digits=sigfigs), digits=sig.dec, format="fg", flag="#")
        out[a] <- strtrim(out[a], sig.dec + c(1, 2)[grepl("-", out[a], fixed=TRUE) + 1])
      }
    }
  }else{
    for(a in 1:length(values)){
      if(values[a]==1){
        out[a] <- paste0("1.", paste0(rep(0, sigfigs), collapse=""))
      }else if((values[a] < as.numeric(paste0("0.", paste0(rep(0, (sigfigs-1)), collapse=""), "1")))){
        out[a] <- paste0("p<0.", paste0(rep(0, (sigfigs-1)), collapse=""), "1")
      }else{
        sig.dec <- (which(strsplit(as.character(values[a]), "")[[1]]==".")-1)+sigfigs
        out[a] <- formatC(round(values[a], digits=sigfigs), digits=sig.dec, format="fg", flag="#")
        out[a] <- paste0("p=", strtrim(out[a], sig.dec + c(1, 2)[grepl("-", out[a], fixed=TRUE) + 1]))
      }
    }
  }
  return(out)
  # print(sig.dec)
  # out <- gsub("\\.$", "",
  #             formatC(round(values, digits=sigfigs),
  #                     digits=which(strsplit(as.character(values), "")[[1]]==".")+1, format="fg", flag="#"))
  # out[grepl(".", out, fixed=TRUE)] <- strtrim(out[grepl(".", out, fixed=TRUE)],
  #                                               sig.dec + c(1, 2)[grepl("-", out, fixed=TRUE) + 1])
  # return(out)
}
# sigfill(c(1000.453, 0.009))
```


# Trans Samples in Dataframe

```{r}
sample.type.rename.data.frame <- function(dataframe, column=NA){
  if(is.na(column)){
    for(a in 1:nrow(dataframe)){
      if(dataframe[a, "Sink"]=="BNA"||dataframe[a, "Sink"]=="0BNA"||dataframe[a, "Sink"]=="WBNA"){
        dataframe[a, "Sink"] <- "Infant nasal"
      }else if(dataframe[a, "Sink"]=="BSA"||dataframe[a, "Sink"]=="0BSA"||dataframe[a, "Sink"]=="WBSA"){
        dataframe[a, "Sink"] <- "Infant saliva"
      }else if(dataframe[a, "Sink"]=="BST"||dataframe[a, "Sink"]=="0BST"||dataframe[a, "Sink"]=="WBST"){
        dataframe[a, "Sink"] <- "Infant stool"
      }
      if(dataframe[a, "Source"]=="MNA"||dataframe[a, "Source"]=="0MNA"||dataframe[a, "Source"]=="WMNA"){
        dataframe[a, "Source"] <- "Mother nasal"
      }else if(dataframe[a, "Source"]=="MSA"||dataframe[a, "Source"]=="0MSA"||dataframe[a, "Source"]=="WMSA"){
        dataframe[a, "Source"] <- "Mother saliva"
      }else if(dataframe[a, "Source"]=="MBM"||dataframe[a, "Source"]=="0MBM"||dataframe[a, "Source"]=="WMBM"){
        dataframe[a, "Source"] <- "Mother milk"
      }else if(dataframe[a, "Source"]=="MAS"||dataframe[a, "Source"]=="0MAS"||dataframe[a, "Source"]=="WMAS"){
        dataframe[a, "Source"] <- "Mother skin"
      }
    }
  }else{
    for(a in 1:nrow(dataframe)){
      if(dataframe[a, column]=="BNA"||dataframe[a, column]=="0BNA"||dataframe[a, column]=="WBNA"){
        dataframe[a, column] <- "Infant nasal"
      }else if(dataframe[a, column]=="BSA"||dataframe[a, column]=="0BSA"||dataframe[a, column]=="WBSA"){
        dataframe[a, column] <- "Infant saliva"
      }else if(dataframe[a, column]=="BST"||dataframe[a, column]=="0BST"||dataframe[a, column]=="WBST"){
        dataframe[a, column] <- "Infant stool"
      }
      if(dataframe[a, column]=="MNA"||dataframe[a, column]=="0MNA"||dataframe[a, column]=="WMNA"){
        dataframe[a, column] <- "Mother nasal"
      }else if(dataframe[a, column]=="MSA"||dataframe[a, column]=="0MSA"||dataframe[a, column]=="WMSA"){
        dataframe[a, column] <- "Mother saliva"
      }else if(dataframe[a, column]=="MBM"||dataframe[a, column]=="0MBM"||dataframe[a, column]=="WMBM"){
        dataframe[a, column] <- "Mother milk"
      }else if(dataframe[a, column]=="MAS"||dataframe[a, column]=="0MAS"||dataframe[a, column]=="WMAS"){
        dataframe[a, column] <- "Mother skin"
      }
    }
  }
  
  return(dataframe)
}
```


## Data Summary

```{r}
data.summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean=mean(x[[col]], na.rm=TRUE),
      sd=sd(x[[col]], na.rm=TRUE))
  }
  data_sum <- ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean"=varname))
 return(data_sum)
}
```


## Add number of taxa

```{r}
add.taxa.number <- function(phyloseq){
  sample_data(phyloseq)[, "samID"] <- sample_names(phyloseq)
  sample.frame <- sample.to.data.frame(phyloseq)
  for(a in 1:nrow(sample.to.data.frame(phyloseq))){
    phyloseq.sub <- subset.object(phyloseq, sample.frame[a,"samID"], "samID")
    sample.frame.sub <- sample.to.data.frame(phyloseq.sub)
    sample_data(phyloseq)[rownames(sample.frame)[a], "taxa.number"] <- sum(otu.to.data.frame(phyloseq.sub) != 0)
  }
  sample_data(phyloseq) <- sample_data(phyloseq)[, -c(which(colnames(sample_data(phyloseq))=="samID"))]
  return(phyloseq)
}
```

## Which Col Name

```{r}
which.col.name <- function(dataframe, col.name){
  return(which(colnames(dataframe)==col.name))
}
```

## Round to

```{r}
round.to <- function(value, to, top.bottom=NA){
  if(is.na(top.bottom)){
    return(round(value/to)*to)
  }else if(top.bottom=="top"){
    return(ceiling(value/to)*to)
  }else if(top.bottom=="bottom"){
    return(floor(value/to)*to)
  }
}
```

## Find break limit

```{r}
find.break.limit <- function(value){
  if(value<=500000){
    test <- TRUE
    a <- 1
    while(test){
      if(value<=(500000/(a)) && value>=(200000/(a))){
        test <- FALSE
        return((100000/(a)))
      }else if(value<=(200000/(a)) && value>=(100000/(a))){
        test <- FALSE
        return((50000/(a)))
      }else if(value<=(100000/(a)) && value>(50000/(a))){
        test <- FALSE
        return((25000/(a)))
      }
      a <- (a*10)
    }
  }
}
```

```{r}
### Reassign NA to unclassified ###
na.to.unclassified <- function(phyloseq){
        cat("\n  ", paste("Reassign NA to unclassified"))
  na.table <- as.data.frame(tax_table(phyloseq))
  for(i in 1:nrow(tax_table(phyloseq))){
    for(j in 2:7){
      if(is.na(tax_table(phyloseq)[i, j])){
        k=j
        for(k in k:7){
          tax_table(phyloseq)[i, k] <- paste(tax_table(phyloseq)[i, j-1], "Unclassified", 
                                              colnames(tax_table(phyloseq))[j], rownames(tax_table(phyloseq))[i])
        }
      }
    }
  }
  tax_table(phyloseq) <- tax_table(phyloseq)[!is.na(tax_table(phyloseq)[, 1]), ]
  return(phyloseq)
}
```

## Reword unclassified
```{r}
reword.unclassified <- function(phyloseq){
  phyloseq.tax <- phyloseq
  tax <- tax_table(phyloseq.tax)
  for(a in 1:nrow(tax)){
    if(str_detect(tax[a, "Species"], "Unclassified")==TRUE){
      tax[a, "Species"] <- paste("Unclassified", str_split(tax[a, "Species"], " Unclassified ")[[1]][1])
    }
    if(str_detect(tax[a, "Genus"], "Unclassified")==TRUE){
      if(str_detect(tax[a, "Genus"], "Bacteria")==TRUE){
        tax[a, "Genus"] <- paste("Unclassified", str_split(str_split(tax[a, "Genus"], " Unclassified ")[[1]][2], " ")[[1]][2])
      }else{
        tax[a, "Genus"] <- paste0("Unclassified\n", str_split(tax[a, "Genus"], " Unclassified ")[[1]][1], " ",
                                 str_split(str_split(tax[a, "Genus"], " Unclassified ")[[1]][2], " ")[[1]][2])
      }
    }
    # if(str_detect(tax[a, "Phylum"], "Unclassified")==TRUE){
    #   if(str_detect(tax[a, "Phylum"], "Bacteria")==TRUE){
    #     tax[a, "Phylum"] <- paste("Unclassified", str_split(str_split(tax[a, "Phylum"], " Unclassified ")[[1]][2], " ")[[1]][2])
    #   }else{
    #     tax[a, "Phylum"] <- paste0("Unclassified\n", str_split(tax[a, "Phylum"], " Unclassified ")[[1]][1], " ",
    #                              str_split(str_split(tax[a, "Phylum"], " Unclassified ")[[1]][2], " ")[[1]][2])
    #   }
    # }
  }
  tax_table(phyloseq.tax) <- tax_table(tax)
  return(phyloseq.tax)
}
```

# Color Functions 

## Color List

```{r Color List}
color.list <- function(n, other=FALSE){
  # colors <- c("#900000", "#B34A00", "#C9AB00", "#2A6116", "#001BA5", "#4F02A0", "#6902A0")
  # colors <- c("#900000", "#B34A00", "#C9AB00", "#2A6116", "#001BA5", "#4F02A0", "#8302A0")
  # colors <- c("#900000", "#B34A00", "#C9AB00", "#2A6116", "#001BA5", "#4F02A0", "#9602A0")
  colors <- c("#900000", "#B34A00", "#C9AB00", "#2A6116", "#001BA5", "#4F02A0", "#A00281")
  if(other==TRUE){
    colors <- c("#900000", "#B34A00", "#C9AB00", "#2A6116", "#165061", "#001BA5", "#4F02A0", "#A00281", "#382417")
  }
  
  color.list <- "#FFFFFF00"
  for(a in 1:length(colors)){
    my_col_alpha_all <- character()
    if(n<=5){
      offset=(0+0.5)
      my_col_alpha_all <- adjustcolor(colors[a], offset=c(offset, offset, offset, offset))
    }else if(n==20){
      for(b in 1:3) {
        offset=(0+((b-1)*0.25))
        my_col_alpha_all[b] <- adjustcolor(colors[a], offset=c(offset, offset, offset, offset))
      }
    }else{
      # for(b in 1:(ceiling(n/20)*3)){
      for(b in 1:(ceiling(n/7))){
        offset=(0+((b-1)*(0.25/ceiling(n/25))))
        my_col_alpha_all[b] <- adjustcolor(colors[a], offset=c(offset, offset, offset, offset))
      }
    }
    # show_col(my_col_alpha_all)
    color.list <- c(color.list, my_col_alpha_all)
  }
  # set.seed(872436)
  # x_rand <- sample(color.list)
  # show_col(color.list)
  return(color.list)
}
```

## Color List Gradient

```{r Color List Gradient}
color.list.grad <- function(n, color.list){
  color <- c(color.list)
  color.grad <- c()
  if(length(color.list)==1){
    for(a in 1:(n)){
      offset=(0+((a-1)/((n)+2)))
      color.grad[a] <- adjustcolor(color.list[1], offset=c(offset, offset, offset, offset))
    }
  }else if(length(color.grad)==1){
    for(a in 1:(n/2)){
      offset=(0+((a-1)/((n/2)+2)))
      color.grad[a] <- adjustcolor(color.list[1], offset=c(offset, offset, offset, offset))
    }
    for(b in (n/2):(n)){
      offset=(0+(((b-(n/2))-1)/((n/2)+2)))
      color.grad[(n/2)+(n-b)] <- adjustcolor(color.list[2], offset=c(offset, offset, offset, offset))
    }
  }
  
  # show_col(color.grad)
  return(color.grad)
}

show_col(color.list.grad(8,color.list(20)[2]))
# color.list.grad(46)
```
